Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-06 workflow/workflow.Rmd
rm c7

```{r norm}
norm <- assays(se)$normalizedValues
stopifnot(sum(is.infinite(norm))==0)
norm[1:3,1:3]
```

@@

```{r}
our_cl <- primaryClusterNamed(ceObj)
cl = our_cl[our_cl != "-1"]
pal = pal[names(pal) != "-1"]
X <- W[our_cl != "-1", ]
mds <- cmdscale(dist(X), eig = TRUE, k = 4)
X <- mds$points

@@

In the workflow, we recover a reasonable ordering of the clusters using the unsupervised version of slingshot. However, in some other cases, we have noticed that we need to give more guidance to the algorithm to find the correct ordering. `getLineages` has the option for the user to provide known end cluster(s). Here is the code to use `slingshot` in a supervised setting, where we know that clusters `c8` and `c6` represent terminal cell fates.

@@

```{r fitgam}
t <- pseudotime(lineages)[,1]
y <- assays(se)$normalizedValues[, our_cl != "-1"]
gam.pval <- apply(y,1,function(z){
  d <- data.frame(z=z, t=t)
  tmp <- gam(z ~ lo(t), data=d)
  p <- summary(tmp)[4][[1]][1,5]
  p
})
```

>>>>

```{r norm}
norm <- assays(se)$normalizedValues
norm[1:3,1:3]
```

@@

```{r}
our_cl <- primaryClusterNamed(ceObj)
cl = our_cl[!our_cl %in% c("-1", "c7")]
pal = pal[!names(pal) %in% c("-1", "c7")]
X <- W[!our_cl %in% c("-1", "c7"), ]
mds <- cmdscale(dist(X), eig = TRUE, k = 4)
X <- mds$points

@@

In the workflow, we recover a reasonable ordering of the clusters using the unsupervised version of slingshot. However, in some other cases, we have noticed that we need to give more guidance to the algorithm to find the correct ordering. `getLineages` has the option for the user to provide known end cluster(s). Here is the code to use `slingshot` in a supervised setting, where we know that clusters `c3` and `c6` represent terminal cell fates.

@@

```{r fitgam}
t <- pseudotime(lineages)[,1]
y <- assays(se)$normalizedValues[, !our_cl %in% c("-1", "c7")]
gam.pval <- apply(y,1,function(z){
  d <- data.frame(z=z, t=t)
  tmp <- gam(z ~ lo(t), data=d)
  p <- summary(tmp)[4][[1]][1,5]
  p
})
```
